HPC--101\\Onboarding

### 2016-01-23 hpc_101/paper.tex
Clarification on time format Removal of confusing cd in the example slurm scripts

\subsection{Transferring Files}
\begin{frame}
	\frametitle{Available File Transfer Protocols}
	\begin{itemize}
		\item The cluster has the following options for transferring files:
		\begin{itemize}
			\item[--] scp (RCP$+$SSH protocol)
			\item[--] rsync (rsync protocol with SSH transport)
			\item[--] SFTP (SSH FTP protocol)
			\item[--] \href{https://www.globus.org/}{Globus} (Grid FTP protocol)
		\end{itemize}
		\item All options are widely used, and have clients that can be found for on most major operating systems
%               \item Please see the the CI website for links to several different clients?                 
	\end{itemize}
	\btVFill
	\begin{center}
		SFTP, scp, and rsync are fairly common on Linux systems,~\\but Globus is not as common~\ldots
	\end{center}

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=MPI\_example
\#SBATCH \ddash{}partition=exclusive.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=4
\#SBATCH \ddash{}tasks-per-node=20
\#SBATCH \ddash{}cpus-per-task=1
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                             
\#SBATCH \ddash{}error=hello-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=hello-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

cd \$SLURM\_SUBMIT\_DIR
srun  -n \$\{SLURM\_NTASKS\}  ./hello\_mpi.intel 
\end{semiverbatim}
\end{frame}

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                              
\#SBATCH \ddash{}error=hello-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=hello-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

cd \$SLURM\_SUBMIT\_DIR
./hello\_world
\end{semiverbatim}
\end{frame}

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                               
\#SBATCH \ddash{}error=buzz-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=buzz-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

cd \$SLURM\_SUBMIT\_DIR
./worker\_bee -i input\_\$\{SLURM_ARRAY_TASK_ID\}.flower -o output\_\$\{SLURM_ARRAY_TASK_ID\}.honey
\end{semiverbatim}
\end{frame}

@@

\subsection{Lustre Filesystem Purge Policies}
\begin{frame}
\frametitle{{\lustre} Filesystem Purge Policies}
Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have currently implemented a purge policy, for any file that is older than 90 days.
\begin{itemize}
 \item Which of my directories are subject to the purge policy?
   \begin{itemize}
   \item \textbf{Answer:} All files and folders found in \ctilde/lus/ are subject to the 90 day purge policy.  Symlinks are excluded from the purge, and are not followed by the purge bot.  
   \end{itemize}
\item How frequently are files for purging identified?
   \begin{itemize}
   \item \textbf{Answer:} Current frequency is every other month, but the frequency many increase or decrease based on the fill rate of the {\lustre} filesystem 
	\end{itemize}
\end{itemize}
\btVFill
\begin{center}
\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
\end{center}

@@

\item HELP! My job needs more time and does not support checkpointing.  What can I do?
  \begin{itemize}\tiny
  \item \textbf{Answer:} We understand that jobs may not all fit within the 3 day timelimit or unforeseen issues during the execution can cause a job to run long.  The {\citeam} does review and potentially approves requests to extend jobs in a one off fashion.  A request to extend a job can be denied, since we need to take into account factor such as: how busy the cluster is, the number of time extension requests a user has made in recent history.\\If it is known before the job is submitted that more than 3 days is required, we would ask that you contact us first so we can verify that you truly will need more time.\\If a job is already running and just doesn't look like it will complete in time, please send us a request with the jobid number and what you want the job extended to e.g., please extend my jobs run time to 7 days.\\Please remember the {\citeam} is small and we are also human.  Depending on when you make your request we may not be able to immediately respond or act.  It is best to make your request at the first signs you need more time, in hopes that you can provide us with ample time to act.
  \end{itemize}

>>>>

\subsection{Transferring Files}
\begin{frame}
	\frametitle{Available File Transfer Protocols}
	\begin{itemize}
		\item The cluster has the following options for transferring files:
		\begin{itemize}
			\item[--] scp (RCP$+$SSH protocol)
			\item[--] rsync (rsync protocol with SSH transport)
			\item[--] SFTP (SSH FTP protocol) -- Filezilla, Cyberduck
			\item[--] \href{https://www.globus.org/}{Globus} (Grid FTP protocol)
		\end{itemize}
		\item All options are widely used, and have clients that can be found for on most major operating systems
%               \item Please see the the CI website for links to several different clients?                 
	\end{itemize}
	\btVFill
	\begin{center}
		SFTP, scp, and rsync are fairly common on Linux systems,~\\but Globus is not as common~\ldots
	\end{center}

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=MPI\_example
\#SBATCH \ddash{}partition=exclusive.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=4
\#SBATCH \ddash{}tasks-per-node=20
\#SBATCH \ddash{}cpus-per-task=1
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                             
\#SBATCH \ddash{}error=hello-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=hello-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

srun  -n \$\{SLURM\_NTASKS\}  ./hello\_mpi.intel 
\end{semiverbatim}
\end{frame}

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                              
\#SBATCH \ddash{}error=hello-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=hello-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

./hello\_world
\end{semiverbatim}
\end{frame}

@@

\#!/bin/sh
\#SBATCH \ddash{}job-name=example
\#SBATCH \ddash{}partition=community.q
\#\# 3 day max run time for community.q, kill.q, exclusive.q, and htc.q.  1 Hour max run time for sb.q
\#SBATCH \ddash{}time=3-00:00:00 ## time format is DD-HH:MM:SS
\#\# task-per-node x cpus-per-task should not typically exceed core count on an individual node 
\#SBATCH \ddash{}nodes=1
\#SBATCH \ddash{}tasks-per-node=1
\#SBATCH \ddash{}cpus-per-task=5
\#SBATCH \ddash{}mem-per-cpu=6400 \#\# max of 6400 for standard nodes, max of 26214 for large memory nodes                                                                                                                                               
\#SBATCH \ddash{}error=buzz-\%A\_\%a.err \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#SBATCH \ddash{}output=buzz-\%A\_\%a.out \#\# \%A - filled with jobid. \%a - filled with job arrayid
\#\# Useful for remote notification
\#SBATCH \ddash{}mail-type=BEGIN,END,FAIL,REQUEUE,TIME\_LIMIT\_80
\#SBATCH \ddash{}mail-user=user@test.org

@@

./worker\_bee -i input\_\$\{SLURM_ARRAY_TASK_ID\}.flower -o output\_\$\{SLURM_ARRAY_TASK_ID\}.honey
\end{semiverbatim}
\end{frame}

@@

\subsection{Lustre Filesystem Purge Policies}
\begin{frame}
\frametitle{{\lustre} Filesystem Purge Policies}
Due to users not having any quotas on the {\lustre} filesystem, we need some policy in place which removes older files from the system.  To accomplish this, we have currently implemented a purge policy, for any file that is older than 90 days.
\begin{itemize}
 \item Which of my directories are subject to the purge policy?
   \begin{itemize}
   \item \textbf{Answer:} All files and folders found in \ctilde/lus/ are subject to the 90 day purge policy.  Symlinks are excluded from the purge, and are not followed by the purge bot.  
   \end{itemize}
\item How frequently are files for purging identified?
   \begin{itemize}
   \item \textbf{Answer:} Current frequency is every other month, but the frequency many increase or decrease based on the fill rate of the {\lustre} filesystem 
	\end{itemize}
\end{itemize}
\btVFill
\begin{center}
\footnotesize \textbf{\emph{Purge policy is subject to change~\\Users will be notified via email prior to changes taking effect}}
\end{center}
\end{frame}

@@

\item HELP! My job needs more time and does not support check-pointing.  What can I do?
  \begin{itemize}\tiny
  \item \textbf{Answer:} We understand that jobs may not all fit within the 3 day timelimit or unforeseen issues during the execution can cause a job to run long.  The {\citeam} does review and potentially approves requests to extend jobs in a one off fashion.  A request to extend a job can be denied, since we need to take into account factor such as: how busy the cluster is, the number of time extension requests a user has made in recent history.\\If it is known before the job is submitted that more than 3 days is required, we would ask that you contact us first so we can verify that you truly will need more time.\\If a job is already running and just doesn't look like it will complete in time, please send us a request with the jobid number and what you want the job extended to e.g., please extend my jobs run time to 7 days.\\Please remember the {\citeam} is small and we are also human.  Depending on when you make your request we may not be able to immediately respond or act.  It is best to make your request at the first signs you need more time, in hopes that you can provide us with ample time to act.
  \end{itemize}
